On the combination of Set Functions and Failures

### 2015-11-17 docs/src/usage.tex
Bug fix in reading of RC arguments

There are also some specific options that can be used
when invoking \CYS:
\begin{description}
\item[\code{--noreadline}:]
Do not use input line editing (see Section~\ref{sec-readline}).
\item[\code{-Dname=val}:]
Overwrite values defined in the configuration file \ccode{.kics2rc}
(see Section~\ref{sec-customization}),
where \code{name} is a property defined in the configuration file
and \code{val} its new value.
\end{description}

>>>>

There are also some specific options that can be used
when invoking \CYS:
\begin{description}
\item[\fbox{\code{--noreadline}}] (if used, this must be the first option):
Do not use input line editing (see Section~\ref{sec-readline}).
\item[\fbox{\code{-Dname=val}}]
(these options must come before any \CYS command):
Overwrite values defined in the configuration file \ccode{.kics2rc}
(see Section~\ref{sec-customization}),
where \code{name} is a property defined in the configuration file
and \code{val} its new value.
\end{description}
